The Importance of Affective States in Privacy Calculus

### 2021-05-01 submission.tex
reformatted

%%
%% These commands are for a JOURNAL article.
%%\acmJournal{TOG}
%%\acmVolume{37}
%%\acmNumber{4}
%%\acmArticle{111}
%%\acmMonth{8}

@@

\section{Methodology}
This is a mixed methods study. Surveys are sent out first to find correlations between privacy preserving behavior and the affective states that reinforce them to varying success. Interviews will be conducted with respondents from the survey who want to participate.
\pagebreak
\subsection{Questionnaires}
\nopagebreak The survey is designed to answer:
\begin{itemize}
    \item What privacy protecting behavior respondents actively engage in (from a list of common ones),
    \item How regular and consistent this behavior is
    \item The extent to which respondents feel good or bad when they engage in privacy-protective behavior
    \item The extent to which respondents feel good or bad when they do not engage in privacy-protective behavior
\end{itemize}

@@

Quantitative data is analyzed to find correlations between behavior and affect.
\subsection{Interviews}
Findings in the quantitative data will be used by interviewers to help guide interviewees through semi-structured interviews. The objective of the interviews is to \textbf{a)} collect detailed descriptions of the affective states that are experienced before, during, and after engaging in privacy-related behavior, and \textbf{b)} explore the extent to which privacy-related behavior is shaped by the affective states surrounding them. Prior to addressing these, the interviewer will establish what the interviewee's privacy-related habits are and the extent of their knowledge about privacy. \\

@@

\includegraphics[width=0.5\textwidth]{concerns}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{biblio}

%%
%% If your work has an appendix, this is the place to put it.
\appendix

>>>>

%%
%% These commands are for a JOURNAL article.
\acmJournal{TOG}
\acmVolume{69}
\acmNumber{420}
\acmArticle{314159}
\acmMonth{5}

@@

\section{Methodology}
This is a mixed methods study. Surveys are sent out first to find correlations
between privacy preserving behavior and the affective states that reinforce them
to varying success. Interviews will be conducted with respondents from the
survey who want to participate.
\subsection{Questionnaires}
\nopagebreak The survey is designed to answer:
\begin{itemize}
    \item What privacy protecting behavior respondents actively engage in (from
	a list of common ones),
    \item How regular and consistent this behavior is
    \item The extent to which respondents feel good or bad when they engage in
	privacy-protective behavior
    \item The extent to which respondents feel good or bad when they do not
	engage in privacy-protective behavior
\end{itemize}

@@

Quantitative data is analyzed to find correlations between behavior and affect.
\subsection{Interviews}
Findings in the quantitative data will be used by interviewers to help guide
interviewees through semi-structured interviews. The objective of the interviews
is to \textbf{a)} collect detailed descriptions of the affective states that are
experienced before, during, and after engaging in privacy-related behavior, and
\textbf{b)} explore the extent to which privacy-related behavior is shaped by
the affective states surrounding them. Prior to addressing these, the
interviewer will establish what the interviewee's privacy-related habits are and
the extent of their knowledge about privacy.

@@

\subsection{Respondents' Privacy Concerns}
On average, respondents reported two privacy concerns of the five that were
suggested. The most common concern---password security---was three times as
popular than the least common concern---email tracking.

Fig. \ref{Univariate Distribution Respondent Concerns} presents the frequency
distribution of all five possible concerns.

\begin{figure}[H]
    \includegraphics[width=0.5\textwidth]{concerns}
    \caption{Frequency distribution for respondents' self-reported privacy
    concerns}
    \label{Univariate Distribution Respondent Concerns}
\end{figure}

%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{biblio}

%% If your work has an appendix, this is the place to put it.
\appendix
